The Transition from Massive Metal Free Stars to Dwarf Galaxies

### 2011-01-20 ms.tex
Started on the results section.  Added halo mass function and galaxy luminosity plot.

These stars have large luminosities on the order of 10$^6 \lsun$,
surface temperatures of $\sim 10^5$ K, and lifetimes of $\sim3$ Myr
\citep{Bond84, Schaerer02}.  Radiation during their main sequence
creates an \hii region with $r \sim 1-3~\mathrm{kpc}$, ionizing the
surrounding intergalactic medium as the virial radii of the host
haloes are $r_{\rm vir} \sim 100 \mathrm{pc}$ \citep{Whalen04,
  Kitayama04, Alvarez06, Abel07}.  The over-pressurized \hii region
drives a $\sim$ 30 \kms~shock, which is 10 times greater than the
escape velocity of a $10^6 \Ms$ halo.  In turn, most of the gas is
expelled from the halo, leaving behind a warm ($3 \times 10^4$ K) and
diffuse (0.5 \cubecm) medium.  In haloes that are encompassed by these
\hii regions and not completely photo-evaporated \citep{Shapiro04,
  whalen08}, the additional free electrons catalyze both \hh~and HD
molecular line cooling \citep{OShea05, Johnson06, Yoshida07,
  McGreer08}, cooling the gas below $\sim$ 100 K and lowering the
Jeans mass to $\sim$ 10--30 \Ms.  These lower-mass, metal-free stars
are called Pop III.2, whereas their more massive counterparts
that form in unheated regions are called Pop III.1 stars
\citep{Norman08}.

A fraction of Pop III stars enrich the surrounding IGM when
they go supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}. The host
halo and the neighboring haloes are then enriched with this ejecta.
The blastwave expands to a radius of a few kpc \citep{Bromm03_SN,
  Wise08_Gal, Greif10} with approximately half of the ejecta falling
back into the adjacent filaments and halos.  The blastwave may induce
star formation in nearby haloes through the compression of the gas
\citep{Shapiro87, Ferrara98, Mackey03}, and the timescales for metal
mixing into the dense gas are many dynamical times \citep{Cen08} for
shock velocities $\lsim 100~\kms$.

@@

Cosmological simulations are useful but computationally expensive to
detangle and study the transition from Pop III to II star formation,
especially the complexities ensuing from hierarchical structure
formation, stellar feedback, and inhomogeneous chemical enrichment.
\citeauthor{Tornatore07} employed smoothed particle hydrodynamics
(SPH) simulations to study this problem and found that Pop III star
formation occurs down to $z=2.5$ in underdense regions.  Their mass
resolution did not allow them to capture star formation in minihalos
($M_{\rm halo} \sim 10^{5-7} \Ms$) that host Pop III stars, which may
have resulted in an underestimate of metal enrichment.  They found a
`Pop III wave' of star formation, where Pop III star formation is
quenched in an inside-out fashion from biased regions to voids, is
however still valid.  \citeauthor{Ricotti08} used a Lagrangian
moving-mesh simulation with radiative, mechanical, and chemical
feedback that resolved minihaloes to find that (i) 1--10\% of the
cosmic volume is chemically enriched, (ii) the gas reservoir in halos
with $M < 10^8 \Ms$ are depleted, (iii) there is a large scatter in
the mass-to-light (M/L) ratios of dwarf galaxies, and (iv) their
luminosity function is relatively flat.  Most recently
\citeauthor{Maio10_Pop32} found that the ratios of Pop III to Pop II
SFRs are insensitive to the exact value of $Z_{\rm cr}$.  In contrast
with \citeauthor{Ricotti08}, only $10^{-8}$ of the simulation volume
is chemically enriched by $z=11$.  This difference of several orders
of magnitude may result from the lack of radiative feedback, which can
expel most of the gas from the host halo before the SN explosion.
Supporting this idea, \citet{Whalen08_SN} found that PISN blastwaves
in neutral halos radiate all of their energy, stalling the shock
within the halo and suppressing outflows.

Here, we present simulations that include both modes of star formation
and their radiative, mechanical, and chemical feedback, extending the
aforementioned previous work on the transition from Pop III to II star
formation and the birth of the first galaxies.  The methods used here
incorporate and link together recent results from metal-enriched and
metal-free star formation, the critical metallicity, and
pair-instability supernovae.  There are some uncertainities in these
input parameters, and we thus run several simulations while varying
these parameters.  This is the first time it has been possible to link
the formation and feedback of the first stars to protogalaxies in a
numerical simulation, resolving the important scales and including the
most important physical effects.

@@

@@

Here we describe our star formation and feedback algorithms, quoting
the parameters used in our fidicual model.  We describe the variations
in these parameters later in Sec. \ref{sec:config}.

@@

The radiation field is evolved with adaptive ray tracing
\citep{Abel02_RT, Wise10} that is based on the HEALPix framework
\citep{HEALPix} and is coupled self-consistently to the hydrodynamics.
Each star particle is a point source of hydrogen ionizing radiation
with the ionizing luminosity equally split between 48 initial rays
(HEALPix level 2).  We use a mono-chromatic spectrum for the radiation
with the energy $E_{\rm ph}$ equaling the luminosity-weighted photon
energy of the spectrum.  For a cosmological simulation that focuses on
galaxies, this does not significantly affect the overall galactic
dynamics \citep[see Sec. 6.3 in][]{Wise10}.  We do not consider helium
singly- and doubly-ionizing radiation.  As the rays propagate from the
source or into a high resolution AMR grid, they are adaptively split
into 4 child rays, increasing the angular resolution of the solution,
when the solid angle of the ray $\theta = 4\pi/(12 \times 4^{L})$ is
larger than 1/3 of the cell area, where $L$ is the HEALPix level.  We
model the \hh~dissociating radiation with an optically-thin, inverse
square profile, centered on all star particles.  In halos with $M
\gsim 10^8 \Ms$, the \hh~column density may become large enough to
self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we may
be underestimating the SFRs in our work.

@@

The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
their lifetime, appropriate for a [Z/H] = $-1.3$ population.  We note
that lower-metallicity stars generate up to 60\% more ionizing photons
and might be underestimating the radiative feedback
\citep{Schaerer03}.  Nonetheless this study provides an excellent
first insight in the transition to Pop II SF, as the metal enrichment
is the key ingredient here.  For SN feedback, these stars generate
$6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ after living for 4 Myr,
which is injected into spheres with a radius of 10 pc, using the same
technique as the Pop III SNe.  However if the resolution of the grid
is less than 10/3 pc, we distribute the energy into a $3^3$ cube
surrounding the star particle.  In addition to numerical stability,
energy distribution across several cells instead of a single cell has
been shown to match cosmic SFRs better in galaxy simulations at lower
redshifts \citep{Smith10}.

@@

We perform five different simulations with the same initial
conditions.  The fiducial model considers (a) primordial cooling with
9 species of hydrogen, helium, and molecular hydrogen, (b) a Pop III
IMF characteristic mass $M_{\rm char}$ = 100 \Ms, and (c) Pop II and
Pop III star formation.  We vary this model with the following
changes:

\begin{itemize}
\item Radiative cooling from metal species.  We calculate a cooling
  curve with CLOUDY \citep{CLOUDY} and use the method of
  \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
  cooling curve.  It is tabulated based on density, temperature,
  electron fraction, and total metallicity.
\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
  the abundance patterns of EMP stars and reionization as constaints,
  the data are best fit with IMFs favoring stars with masses between
  20--130 \Ms \citep{Umeda03, Tumlinson06}.
\item Lyman-Werner radiation background.  We use the semi-analytical
  model of \citet{Wise05}, updated with the 7-year WMAP parameters and
  optical depth to Thompson scattering, to calculate the LW background
  intensity, plotted in Figure \ref{fig:uvb}.  In this semi-analytical
  model, we use a Pop III stellar mass of 100 \Ms, star formation
  efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
  LW radiation from point sources are added to the background.  For
  computational convenience, we fit the background evolution with the
  function
%
  \begin{equation}
    \label{eqn:uvb}
    \log J_{21}(z) = A + Bz - Cz^2 + Dz^3 - Ez^4,
  \end{equation}
%
  where $(A,B,C,D,E) = (-2.356, 0.4562, 0.02680, 5.882 \times 10^{-4},
  -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
  units of $10^{-21}$ \emis.  This fits the model data within 1\% in
  $6 \le z \le 30$ and is consistent with $J_{21}$ values in
  \citet{Trenti09_SFR}.
\item Pop II star formation only.  This model provides a good
  comparison to other works that do not consider \hh~cooling.
\item Pop II star formation only and no molecular hydrogen cooling.
  This model is useful to study the importance of treating Pop III
  star formation and their PISNe.
\end{itemize}

@@

\begin{figure*}
  \plottwo{z7-mosaic0.eps}{z7-mosaic1.eps}
  \caption{\label{fig:z7-mosaic} Redshift 7.}
\end{figure*}

\begin{figure*}
  \plottwo{z8-mosaic0.eps}{z8-mosaic1.eps}
  \caption{\label{fig:z8-mosaic} Redshift 8.}
\end{figure*}

\begin{figure*}
  \plottwo{z10-mosaic0.eps}{z10-mosaic1.eps}
  \caption{\label{fig:z10-mosaic} Redshift 10.}
\end{figure*}

@@

@@

\subsection{Negative feedback from gas loss}

@@

>>>>

These stars have large luminosities on the order of 10$^6 \lsun$,
surface temperatures of $\sim 10^5$ K, and lifetimes of $\sim3$ Myr
\citep{Bond84, Schaerer02}.  Radiation during their main sequence
creates an \hii~region with $r \sim 1-3~\mathrm{kpc}$, ionizing the
surrounding intergalactic medium as the virial radii of the host
haloes are $r_{\rm vir} \sim 100 \mathrm{pc}$ \citep{Whalen04,
  Kitayama04, Alvarez06, Abel07}.  The over-pressurized \hii~region
drives a $\sim$ 30 \kms~shock, which is 10 times greater than the
escape velocity of a $10^6 \Ms$ halo.  In turn, most of the gas is
expelled from the halo, leaving behind a warm ($3 \times 10^4$ K) and
diffuse (0.5 \cubecm) medium.  In haloes that are encompassed by these
\hii~regions and not completely photo-evaporated \citep{Shapiro04,
  whalen08}, the additional free electrons catalyze both \hh~and HD
molecular line cooling \citep{OShea05, Johnson06, Yoshida07,
  McGreer08}, cooling the gas below $\sim$ 100 K and lowering the
Jeans mass to $\sim10-30$ \Ms.  These lower-mass, metal-free stars
are called Pop III.2, whereas their more massive counterparts
that form in unheated regions are called Pop III.1 stars
\citep{Norman08}.

A fraction of Pop III stars enrich the surrounding IGM when
they go supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}. The host
halo and the neighboring haloes are then enriched with this ejecta.
The blastwave expands to a radius of a few kpc \citep{Bromm03_SN,
  Wise08_Gal, Greif10} with approximately half of the ejecta falling
back into the adjacent filaments and haloes.  The blastwave may induce
star formation in nearby haloes through the compression of the gas
\citep{Shapiro87, Ferrara98, Mackey03}, and the timescales for metal
mixing into the dense gas are many dynamical times \citep{Cen08} for
shock velocities $\lsim 100~\kms$.

@@

Cosmological simulations are useful but computationally expensive to
detangle and study the transition from Pop III to II star formation,
especially the complexities ensuing from hierarchical structure
formation, stellar feedback, and inhomogeneous chemical enrichment.
\citeauthor{Tornatore07} employed smoothed particle hydrodynamics
(SPH) simulations to study this problem and found that Pop III star
formation occurs down to $z=2.5$ in underdense regions.  Their mass
resolution did not allow them to capture star formation in minihaloes
($M_{\rm halo} \sim 10^{5-7} \Ms$) that host Pop III stars, which may
have resulted in an underestimate of metal enrichment.  They found a
`Pop III wave' of star formation, where Pop III star formation is
quenched in an inside-out fashion from biased regions to voids, is
however still valid.  \citeauthor{Ricotti08} used a Lagrangian
moving-mesh simulation with radiative, mechanical, and chemical
feedback that resolved minihaloes to find that (i) 1--10\% of the
cosmic volume is chemically enriched, (ii) the gas reservoir in haloes
with $M < 10^8 \Ms$ are depleted, (iii) there is a large scatter in
the mass-to-light (M/L) ratios of dwarf galaxies, and (iv) their
luminosity function is relatively flat.  Most recently
\citeauthor{Maio10_Pop32} found that the ratios of Pop III to Pop II
SFRs are insensitive to the exact value of $Z_{\rm cr}$.  In contrast
with \citeauthor{Ricotti08}, only $10^{-8}$ of the simulation volume
is chemically enriched by $z=11$.  This difference of several orders
of magnitude may result from the lack of radiative feedback, which can
expel most of the gas from the host halo before the SN explosion.
Supporting this idea, \citet{Whalen08_SN} found that PISN blastwaves
in neutral haloes radiate all of their energy, stalling the shock
within the halo and suppressing outflows.

Here, we present simulations that include both modes of star formation
and their radiative, mechanical, and chemical feedback, extending the
aforementioned previous work on the transition from Pop III to II star
formation and the birth of the first galaxies.  The methods used here
incorporate and link together recent results from metal-enriched and
metal-free star formation, the critical metallicity, and
pair-instability supernovae.  There are some uncertainities in these
input parameters, and we thus run several simulations while varying
these parameters.  This is the first time it has been possible to link
the formation and feedback of the first stars to protogalaxies in a
numerical simulation, resolving the important scales and including the
most important physical effects.  This is the first paper in series
that focuses on the formation and properties of high-redshift dwarf
galaxies.

@@

In this section, we describe our cosmological radiation hydrodynamics
simulation suite with sub-pc resolution, focusing on first the
formation and feedback of Pop III stars, the transition to Pop II star
formation, and finally the formation of the first galaxies.  We then
detail our star formation and feedback algorithms.  We run a total of
eight different simulations, varying physical parameters.  In the
following description, we quote the parameters used in our fidicual
model and describe their variations later in Sec. \ref{sec:config}.

@@

@@

The radiation field is evolved with adaptive ray tracing
\citep{Abel02_RT, Wise10} that is based on the HEALPix framework
\citep{HEALPix} and is coupled self-consistently to the hydrodynamics.
Each star particle is a point source of hydrogen ionizing radiation
with the ionizing luminosity equally split between 48 initial rays
(HEALPix level 2).  We use a mono-chromatic spectrum for the radiation
with the energy $E_{\rm ph}$ equaling the luminosity-weighted photon
energy of the spectrum.  For a cosmological simulation that focuses on
galaxies, this does not significantly affect the overall galactic
dynamics \citep[see Sec. 6.3 in][]{Wise10}.  We do not consider helium
singly- and doubly-ionizing radiation.  As the rays propagate from the
source or into a high resolution AMR grid, they are adaptively split
into 4 child rays, increasing the angular resolution of the solution,
when the solid angle of the ray $\theta = 4\pi/(12 \times 4^{L})$ is
larger than 1/3 of the cell area, where $L$ is the HEALPix level.  We
model the \hh~dissociating radiation with an optically-thin, inverse
square profile, centered on all star particles.  In haloes with $M
\gsim 10^8 \Ms$, the \hh~column density may become large enough to
self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we may
be underestimating the SFRs in our work.

@@

The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
their lifetime and $E_{\rm ph} = 21.6$ eV, appropriate for a [Z/H] =
$-1.3$ population.  We note that lower-metallicity stars generate up
to 60\% more ionizing photons and might be underestimating the
radiative feedback \citep{Schaerer03}.  Nonetheless this study
provides an excellent first insight in the transition to Pop II SF, as
the metal enrichment is the key ingredient here.  For SN feedback,
these stars generate $6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$
after living for 4 Myr, which is injected into spheres with a radius
of 10 pc, using the same technique as the Pop III SNe.  However if the
resolution of the grid is less than 10/3 pc, we distribute the energy
into a $3^3$ cube surrounding the star particle.  In addition to
numerical stability, energy distribution across several cells instead
of a single cell has been shown to match cosmic SFRs better in galaxy
simulations at lower redshifts \citep{Smith10}.

@@

We perform eight different simulations with the same initial
conditions.  The fiducial model considers (a) primordial cooling with
9 species of hydrogen, helium, and molecular hydrogen, (b) a Pop III
IMF characteristic mass $M_{\rm char}$ = 100 \Ms, and (c) Pop II and
Pop III star formation.  We vary this model with the following
changes:

\begin{enumerate}
\item Radiative cooling from metal species.  We calculate a cooling
  curve with CLOUDY \citep{CLOUDY} and use the method of
  \citep{2008MNRAS.385.1443S}.  Solar abundances were used in the
  cooling curve.  It is tabulated based on density, temperature,
  electron fraction, and total metallicity.
\item A critical metallicity of [Z/H] = --5 and --6, accounting for
  the case where dust cooling can induce low-mass fragmentation in
  these lower metallicities \citep{Omukai05, Schneider06_Frag}.
\item Pop III IMF characteristic mass $M_{\rm char}$ = 40 \Ms.  Using
  the abundance patterns of EMP stars and reionization as constaints,
  the data are best fit with IMFs favoring stars with masses between
  20--130 \Ms \citep{Umeda03, Tumlinson06}.
\item Lyman-Werner radiation background.  We use the semi-analytical
  model of \citet{Wise05}, updated with the 7-year WMAP parameters and
  optical depth to Thompson scattering, to calculate the LW background
  intensity, plotted in Figure \ref{fig:uvb}.  In this semi-analytical
  model, we use a Pop III stellar mass of 100 \Ms, star formation
  efficiency of 0.005, and escape fraction of 0.2 \citep{Wise09}.  The
  LW radiation from point sources are added to the background.  The
  intensity decreases after $z \sim 14$ because Pop II star formation
  becomes dominant, which produce less LW specific luminosity than Pop
  III stars that have surface temperatures of $T = 10^5$ K.  For
  computational convenience, we fit the background evolution with the
  function
%
  \begin{equation}
    \label{eqn:uvb}
    \log J_{21}(z) = A + Bz - Cz^2 + Dz^3 - Ez^4,
  \end{equation}
%
  where $(A,B,C,D,E) = (-2.356, 0.4562, 0.02680, 5.882 \times 10^{-4},
  -5.056 \times 10^{-6})$ and $J_{21}$ is the specific intensity in
  units of $10^{-21}$ \emis.  This fits the
  model data within 1\% in $6 \le z \le 30$ and is consistent with
  $J_{21}$ values in \citet{Trenti09_SFR}.
\item Pop II star formation only.  This model is useful to study the
  importance of treating Pop III star formation as single stars and
  their pair-instability and Type II SNe.
\item Pop II star formation only and no molecular hydrogen cooling.
  This model provides a good comparison to larger scale simulations
  where it is not computationally feasible to consider \hh~cooling or
  resolve the necessary scales for Pop III star formation.
\end{enumerate}

By running several simulations with different physical scenarios, we
can quantify the importance of each ingredient in high-redshift dwarf
galaxy formation.  This approach is similar in spirit with many other
galaxy formation simulation suites \citep[e.g.][]{Schaye10,
  Maio10_Pop32}.

@@

\begin{figure}
  \plotone{Lstar.eps}
  \caption{\label{fig:mass_fn} The top panel shows the halo mass
    function of the simulated haloes (points) where the error bars are
    Poisson noise and the solid line is the analytic halo mass
    function of \citet{Warren06}.  The bottom panel depicts the galaxy
    luminosities versus halo DM mass.  Overplotted are constant
    mass-to-light ratios.  The large scatter at low halo masses are
    similar to ones observed in local dSph galaxies.}
\end{figure}

Here we present the gaseous and stellar evolution of the high-redshift
dwarf galaxies that form in our simulations.  To illustrate its global
properties, we show the density-weighted projections of gas density,
temperature, and metallicity at redshifts 15, 12, 10, 8, and 7 in
Figure \ref{fig:evo-mosaic}.  Most apparent is the photo-heating of
IGM over this redshift range, where the ionized fraction is 0.XX at
$z=7$.  The metallicity projections show the growth of metal-enriched
bubbles, starting first with enrichment from Pop III stars.  Then as
time progresses, the haloes enriched within these bubbles above $Z_{\rm
  cr}$ transition to Pop II star formation, enriching their host halo
and surrounding IGM.  In Fig. \ref{fig:mass_fn}, we show the halo mass
function, agreeing well with the analytic halo mass function of
\citet{Warren06}.  We identify the haloes with a friends-of-friends
(FOF) algorithm \citep{Davis85}.  The excess of low-mass haloes below
$M_{\rm DM} = 2 \times 10^6 \Ms$ is most likely associated with the
biased region in the lower-right region in the projections.
Furthermore, the uncertainities in different analytic halo mass
functions \citep[e.g., see][for a comparison]{Reed07} and halo
identification are comparable than these differences.  Also in this
Figure, we display the galaxy luminosities with respect to halo DM
mass found with the FOF halo finder.  Our fidicual model contains 38
galaxies with a total of 3640 Pop II star clusters and captures the
formation of 333 Pop III stars.  Note that the most massive halo
($M_{\rm DM} = 5.2 \times 10^8 \Ms$) is undergoing a starburst at
$z=7$ and has a high $M/L = 3$.  The lower mass galaxies show a spread
in M/L over two orders of magnitude, similar to the observations of
local dSph galaxies \citep[e.g.][]{Strigari08}.

We split our presentation into two sets of analyses.  In one, we focus
on the evolution of the individual halo and galaxy properties of the
10 most massive haloes at $z=7$ to better understand their formation
process and progenitors.  Second, we analyze the statistics of the
star formation and metal enrichment in all 38 galaxies.  We start by
presenting the change in the global halo properties, followed by their
metal enrichment histories.  Lastly we detail their star formation
histories, metallicity distribution functions, and star formation
rates.

@@

To get a visual sense of the mass accretion and metal enrichment
history of the 10 most massive haloes, we show their density-weighted
projections of gas density, temperature, and composite Pop II+III
metallicity at redshifts 7, 8, and 10 in
Fig. \ref{fig:z7-mosaic}--\ref{fig:z10-mosaic}, respectively.  One
common feature of all of the halos represented in these Figure is that
they are embedded in a preheated IGM with the exception of Halo 7 at
$z=10$.  Prior radiative feedback in either the host or nearby halos
created \hii~regions that encompass these halos.  For \hii~regions
without sustained star formation, these so-called relic \hii~regions
recombine and radiatively cool down to $T = 10^3$ K.  Within the
virial radius, one can see that our simulations capture the
multi-phase ISM.  In the density projections, the effects of
photo-evaporation and cloud crushing are clearly seen, which are
caused by the stellar radiative and mechanical feedback, respectively.
The filaments adjacent to the halos are photo-heated to $T = 1-3
\times 10^4$ K, and then their gas escapes into the IGM no longer
being pressure equilibrium with the gravitational potential of the
filament, i.e. Jeans smoothing.  Furthermore, neighboring halos are
photo-evaporated \citep[see][for the level of halo
photo-evaporation]{Wise08_Reion}, resulting in the suppression of
gas-rich satellite haloes.  A good illustration of photo-evaporation
in progress is the cometary structure in the bottom-center of the
density projection of Halo 4 at $z=7$.

\li Something is wrong with the progenitor finder with Halo 9 at $t =
500$ Myr.  See the extreme jump in mass and decrease in gas fraction?

In Fig. \ref{fig:massevo}, we show the total halo mass $M_{\rm tot}$,
stellar mass $M_\star$, and gas fraction $f_{\rm gas} = M_{\rm gas} /
M_{\rm tot}$ of the most massive halos as a function of time.  We
define the halo as a sphere with a radius $r_{200}$, centered on the
DM center-of-mass, with an overdensity of 200 times the cosmic mean
density.  We identify the progenitors of these halos by searching for
the halo in the previous output with the greatest number of shared
particles (all particles in \enzo~have unique identification numbers).
The mass accretion histories of the halos are not atypical from ones
found in cosmological simulations with periods of smooth accretion
from the IGM and filaments with major mergers occasionally occurs,
appearing as jumps in $M_{\rm halo}(z)$.

Even from these visual representations of the data, it is clear that
almost all of the halos are gas-poor with outflows from Pop III star
formation and PISNe having the greatest effect.

\begin{figure*}
  \plottwo{z7-mosaic0.eps}{z7-mosaic1.eps}
  \caption{\label{fig:z7-mosaic} Density-weighted projections of
    density (left), temperature (center), and metallicity (right) of
    the 10 most massive haloes at $z=7$.  The field of view is 5 proper
    kpc, and the circles have a radius of $r_{200}$.  The composite
    metallicity images are constructed in the same fashion as
    Fig. \ref{fig:evo-mosaic}.}
\end{figure*}

\begin{figure*}
  \plottwo{z8-mosaic0.eps}{z8-mosaic1.eps}
  \caption{\label{fig:z8-mosaic} Same as Fig. \ref{fig:z7-mosaic} but
    at $z=8$, showing the progenitors of the 10 most massive haloes at
    $z=7$.}
\end{figure*}

\begin{figure*}
  \plottwo{z10-mosaic0.eps}{z10-mosaic1.eps}
  \caption{\label{fig:z10-mosaic} Same as Fig. \ref{fig:z8-mosaic} at
    $z=10$.}
\end{figure*}

@@

\subsection{Unique details about individual haloes}

@@

\subsection{Metal cooling}

\subsection{Varying the critical metallicity}

\subsection{Characteristic mass of the Pop III IMF}

\subsection{Lyman-Werner radiation background}

\subsection{Neglecting Pop III star formation}

\subsection{Neglecting Pop III star formation and \hh~formation}
